Extreme Value Chapter

### 2022-03-01 Ch3_samplesize/Figures_Ch3.Rmd
Progress

# See it compared to the original theta
nreps_mles_df %>% 
  filter(., thresh_tests < 250) %>% 
  mutate(samp_n_tests = factor(samp_n_tests),
         thresh_tests = factor(thresh_tests)) %>% 
  ggplot(., aes(x = thresh_tests, y = log_St_hat - log(theta), fill = samp_n_tests, color = samp_n_tests)) +
  # facet_wrap(~samp_n_tests, nrow = 1) +
  geom_boxplot(alpha = 0.9) +
  geom_hline(yintercept = 0, color = "red") +
  scale_fill_manual(values = pal_sampsize) +
  scale_color_manual(values = pal_sampsize) +
  labs(x = "Distance level", y = TeX(r'($log(\hat{\theta} / \theta)$)'), subtitle = "Simple Lomax") +
  theme_bw() +
  theme(legend.position = "none") -> a1

nreps_mles_df %>% 
  filter(., thresh_tests >= 250) %>% 
  mutate(samp_n_tests = factor(samp_n_tests),
         thresh_tests = factor(thresh_tests)) %>% 
  ggplot(., aes(x = thresh_tests, y = log_St_hat - log(theta), fill = samp_n_tests, color = samp_n_tests)) +
  # facet_wrap(~samp_n_tests, nrow = 1) +
  geom_boxplot(alpha = 0.9) +
  geom_hline(yintercept = 0, color = "red") +
  scale_fill_manual(values = pal_sampsize) +
  scale_color_manual(values = pal_sampsize) +
  labs(x = "Distance level", y = " ", subtitle = " ") +
  theme_bw() +
  theme(legend.position = "none") -> a2

@@

nreps_mles_df %>% 
  filter(., thresh_tests < 250) %>% 
  mutate(samp_n_tests = factor(samp_n_tests),
         thresh_tests = factor(thresh_tests)) %>% 
  ggplot(., aes(x = thresh_tests, y = log_St_hat2 - log(theta), fill = samp_n_tests, color = samp_n_tests)) +
  # facet_wrap(~samp_n_tests, nrow = 1) +
  geom_boxplot(alpha = 0.9) +
  geom_hline(yintercept = 0, color = "red") +
  scale_fill_manual(values = pal_sampsize, name = "Sample Size") +
  scale_color_manual(values = pal_sampsize, name = "Sample Size") +
  labs(x = "Distance level", y = TeX(r'($log(\hat{\theta} / \theta)$)'), subtitle = "GLM Lomax") +
  theme_bw() +
  theme(legend.position = "none") -> b1

nreps_mles_df %>% 
  filter(., thresh_tests >= 250) %>% 
  mutate(samp_n_tests = factor(samp_n_tests),
         thresh_tests = factor(thresh_tests)) %>% 
  ggplot(., aes(x = thresh_tests, y = log_St_hat2 - log(theta), fill = samp_n_tests, color = samp_n_tests)) +
  # facet_wrap(~samp_n_tests, nrow = 1) +
  geom_boxplot(alpha = 0.9) +
  geom_hline(yintercept = 0, color = "red") +
  scale_fill_manual(values = pal_sampsize, name = "Sample Size") +
  scale_color_manual(values = pal_sampsize, name = "Sample Size") +
  labs(x = "Distance level", y = " ", subtitle = " ") +
  theme_bw() +
  theme(legend.position = "none") -> b2

b2

@@

ableg <- get_legend(b + theme(legend.position = "right"))

@@

```{r fig.height=3, fig.width=7}
nreps_mles_df %>% 
  mutate(samp_n_tests = factor(samp_n_tests),
         thresh_tests = factor(thresh_tests)) %>% 
  group_by(thresh_tests, samp_n_tests) %>% 
  summarize(Eval_theta_hat = mean(log_St_hat2),
            theta = mean(theta),
            bias = Eval_theta_hat - theta) %>% 
  ggplot(., aes(y = bias, x = thresh_tests)) +
  geom_jitter(aes(color = samp_n_tests), size = 3, alpha = 0.9, width = 0.1) +
  geom_hline(yintercept = 0, color = "red") +
  scale_color_manual(values = pal_sampsize, name = "Sample Size") +
  labs(x = "Long-distance level", y = "Bias", title = "GLM Lomax") +
  theme_bw()

nreps_mles_df %>% 
  mutate(samp_n_tests = factor(samp_n_tests),
         thresh_tests = factor(thresh_tests),
         theta_diff= log_St_hat2 - theta) %>% 
  group_by(thresh_tests, samp_n_tests) %>% 
  summarize(Eval_theta_hat = mean(log_St_hat2),
            MSE = mean(theta_diff)^2,
            theta = mean(theta),
            bias = Eval_theta_hat - theta) %>% 
  ggplot(., aes(y = MSE, x = thresh_tests)) +
  geom_jitter(aes(color = samp_n_tests), size = 3, alpha = 0.9, width = 0.1) +
  geom_hline(yintercept = 0, color = "red") +
  scale_color_manual(values = pal_sampsize, name = "Sample Size") +
  labs(x = "Long-distance level", y = "MSE", title = "GLM Lomax") +
  theme_bw()

>>>>

# See it compared to the original theta
nreps_mles_df %>% 
  filter(., thresh_tests < 500) %>% 
  mutate(samp_n_tests = factor(samp_n_tests),
         thresh_tests = factor(thresh_tests)) %>% 
  ggplot(., aes(x = thresh_tests, y = log_St_hat - log(theta), fill = samp_n_tests, color = samp_n_tests)) +
  # facet_wrap(~samp_n_tests, nrow = 1) +
  geom_boxplot(alpha = 0.9) +
  geom_hline(yintercept = 0, color = "red") +
  scale_fill_manual(values = pal_sampsize) +
  scale_color_manual(values = pal_sampsize) +
  labs(x = "Distance level", y = TeX(r'($log(\hat{\theta} / \theta)$)'), subtitle = "Simple Lomax") +
  theme_bw() +
  theme(legend.position = "none") -> a1

nreps_mles_df %>% 
  filter(., thresh_tests >= 500) %>% 
  mutate(samp_n_tests = factor(samp_n_tests),
         thresh_tests = factor(thresh_tests)) %>% 
  ggplot(., aes(x = thresh_tests, y = log_St_hat - log(theta), fill = samp_n_tests, color = samp_n_tests)) +
  # facet_wrap(~samp_n_tests, nrow = 1) +
  geom_boxplot(alpha = 0.9) +
  geom_hline(yintercept = 0, color = "red") +
  scale_fill_manual(values = pal_sampsize) +
  scale_color_manual(values = pal_sampsize) +
  labs(x = "Distance level", y = " ", subtitle = " ") +
  theme_bw() +
  theme(legend.position = "none") -> a2

@@

nreps_mles_df %>% 
  filter(., thresh_tests < 500) %>% 
  mutate(samp_n_tests = factor(samp_n_tests),
         thresh_tests = factor(thresh_tests)) %>% 
  ggplot(., aes(x = thresh_tests, y = log_St_hat2 - log(theta), fill = samp_n_tests, color = samp_n_tests)) +
  # facet_wrap(~samp_n_tests, nrow = 1) +
  geom_boxplot(alpha = 0.9) +
  geom_hline(yintercept = 0, color = "red") +
  scale_fill_manual(values = pal_sampsize, name = "Sample Size") +
  scale_color_manual(values = pal_sampsize, name = "Sample Size") +
  labs(x = "Distance level", y = TeX(r'($log(\hat{\theta} / \theta)$)'), subtitle = "GLM Lomax") +
  theme_bw() +
  theme(legend.position = "none") -> b1

nreps_mles_df %>% 
  filter(., thresh_tests >= 500) %>% 
  mutate(samp_n_tests = factor(samp_n_tests),
         thresh_tests = factor(thresh_tests)) %>% 
  ggplot(., aes(x = thresh_tests, y = log_St_hat2 - log(theta), fill = samp_n_tests, color = samp_n_tests)) +
  # facet_wrap(~samp_n_tests, nrow = 1) +
  geom_boxplot(alpha = 0.9) +
  geom_hline(yintercept = 0, color = "red") +
  scale_fill_manual(values = pal_sampsize, name = "Sample Size") +
  scale_color_manual(values = pal_sampsize, name = "Sample Size") +
  labs(x = "Distance level", y = " ", subtitle = " ") +
  theme_bw() +
  theme(legend.position = "none") -> b2

@@

ableg <- get_legend(b1 + theme(legend.position = "right"))

@@

```{r fig.height=3, fig.width=7}
nreps_mles_df %>% 
  mutate(samp_n_tests = factor(samp_n_tests),
         thresh_tests = factor(thresh_tests)) %>% 
  group_by(thresh_tests, samp_n_tests) %>% 
  summarize(Eval_theta_hat = mean(log_St_hat2),
            theta = mean(theta),
            bias = Eval_theta_hat - theta) %>% 
  ggplot(., aes(y = bias, x = thresh_tests)) +
  geom_jitter(aes(color = samp_n_tests), size = 3, alpha = 0.9, width = 0.1) +
  geom_hline(yintercept = 0, color = "grey") +
  scale_color_manual(values = pal_sampsize, name = "Sample Size") +
  labs(x = "Distance level", y = "Bias", title = "GLM Lomax") +
  theme_bw()

# 
# nreps_mles_df %>% 
#   mutate(samp_n_tests = factor(samp_n_tests),
#          thresh_tests = factor(thresh_tests),
#          theta_diff= log_St_hat2 - theta) %>% 
#   group_by(thresh_tests, samp_n_tests) %>% 
#   summarize(Eval_theta_hat = mean(log_St_hat2),
#             MSE = mean(theta_diff)^2,
#             theta = mean(theta),
#             bias = Eval_theta_hat - theta) %>% 
#   ggplot(., aes(y = MSE, x = thresh_tests)) +
#   geom_jitter(aes(color = samp_n_tests), size = 3, alpha = 0.9, width = 0.1) +
#   geom_hline(yintercept = 0, color = "red") +
#   scale_color_manual(values = pal_sampsize, name = "Sample Size") +
#   labs(x = "Long-distance level", y = "MSE", title = "GLM Lomax") +
#   theme_bw()
